\documentclass{article}
\usepackage{pdfpages}
\usepackage{float}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{amsmath}

\begin{document}

\begin{description}
\item [Name] Emily Horsman
\item [Mac ID] horsmane
\item [Student Number] 400072650
\item [Other Group Members] Tanner Ryan (ryant3)
\item [Supervisors] Dr. Spencer Smith, Dr. Jacques Carette
\end{description}

\section{Project Description}

The goal of our application is to make it easy to monitor and consume data from a variety of common hardware peripherals (e.g., off-the-shelf accelerometers, temperature sensors, moisture sensors, etc). This will include a back-end which manages application logic for microcontrollers connected to peripherals; provides an API for logged sensor data to be consumed by arbitrary applications (machine learning, analysis, etc); and an easily configurable dashboard in a web browser for viewing peripheral data.
\\\\
If we achieve our goal then a user should be able to plug in a new sensor to commonly available microcontrollers and immediately view data from the sensor in their browser after minimal configuration.

\subsection{Highlights and Possible Scope}

\begin{itemize}
    \item Auto-discovery of I\textsuperscript{2}C sensors using the common request-response protocol.
    \item A library for ``Arduino-compatible'' microcontrollers to send sensor data to a back-end.
    \item An API to read and write sensor data via a common interface.
    \item A dashboard in a web browser to interact with hardware peripherals remotely.
    \item A variety of widgets to view data on the dashboard in various formats.
\end{itemize}

\end{document}
