\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{COMPSCI 4ZP6A --- Initial Document}
\fancyhead[R]{Tanner Ryan <ryant3>, 400053060}

\begin{document}

\section*{September Deliverable}

\subsection*{Project Information}

\begin{itemize}
    \item \textbf{Group Member}: Emily Horsman <horsmane>
    \item \textbf{Supervisors}: Dr. Spencer Smith, Dr. Jacques Carette
\end{itemize}

\subsection*{Project Description}

I\textsuperscript{2}C (Inter-Integrated Circuit) is an existing protocol which
enables hardware peripherals to communicate with microcontrollers. Currently,
application-level interfacing with I\textsuperscript{2}C devices requires
implementations that are specific to a particular device. This creates a
significant amount of work when interfacing with different device types.\\

Our group would like to propose a modular system that allows for the
autodiscovery, transport, and ingestion of I\textsuperscript{2}C device data.\\

The primary project goals are as follows: \begin{enumerate}
    \item Peripheral Autodiscovery: automatically detect when a device is
    physically connected to a microcontroller. Allow a user to provision a
    device through a configurable web dashboard with minimal effort.

    \item Data Transport: provide a robust, software-defined transport mechanism
    to allow for real-time, bidirectional communication with
    I\textsuperscript{2}C devices.

    \item Modular ingestion: create a language-agnostic API for users to
    translate raw I\textsuperscript{2}C data into usable data.
\end{enumerate}

The project will be validated through the popular Arduino platform, interfacing
with numerous, low-cost sensors (e.g. temperature, accelerometer, thermal
camera).

\end{document}
